### 2013-02-04 ABD_results.tex
Finished Menger game characterization
Finished 2-tactic, started k-tactic on Cantor tree of spaces

\begin{document}

%%%%%%%%%
%COMMENT%
%%%%%%%%%
\largecomment{
Assume all spaces are locally compact.

@@

}
%%%%%%%%%%%%
%ENDCOMMENT%
%%%%%%%%%%%%

@@

\begin{proof}
Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)$ and $m(x,y,n)$ such that for each $(x,y)$,
\[
\bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
\]

@@

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
\<x_0, s_0\>, \<x', {z_{m(x_0,x_0,|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
\]
is a successful counter to $\sigma$.

Obviously it also clusters at $c$, so we need only show that it is a legal counter to $\sigma$. Note that \[\sigma(\<x', {z_{m(x_i,x',|s_i|)}}^\frown\<1\>\>, \<x_{i+1}, s_{i+1}\>) \subseteq \sigma(\<x_{i+1}, s_{i+1}\>, \<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>)\] since the only difference in input is a higher copy of $x'\in X$.

Suppose $\<x_{i}, s_{i}\>$ was an illegal move. Then for some $j<i$, that move was forbidden by 
\[
\sigma(\<x_{j}, s_{j}\>, \<x', {z_{m(x_{j},x',|s_{j}|)}}^\frown\<1\>\>)
\]
\[
\subseteq 
K^*_{S(x_{j},x',m(x_{j},x',|s_{j}|)+1)} \cup L_{m(x_{j},x',m(x_{j},x',|s_{j}|)+1)}
= \tau(x_j,s_j)
\]
which is a contradiction as it was a legal move against $\tau$.

Finally, consider $\<x',{z_{m(x_i,x',|s_i|)}}^\frown\<1\>\>$. Since the length of ${z_{m(x_i,x',|s_i|)}}^\frown\<1\>$ is longer than $m(x_i,x',|s_i|)$, it's not forbidden by any $L_m$ played by $K$. And since ${z_{m(x_i,x',|s_i|)}}^\frown\<1\>$ is on the antichain $A$ avoided by the $K^*_S$s, it could never have been forbidden at all.
\end{proof}

\begin{proposition}
The above proof can be adapted to prove $K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
\end{proposition}

>>>>

\begin{document}
Assume all spaces are locally compact.

@@

@@

\begin{proof}
Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
  \[
    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq 
    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
  \]
and so we assume
  \[
    \sigma(\<x,s\>,\<y,t\>) =
    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
  \]

@@

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
\]
is a successful counter to $\sigma$.

We will need the fact that:
  \[
    |s_i| <
    m(x_i,x',|s_i|)+1 =
    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>| 
  \]
  \[
    <
    m(x_i,x',m(x_i,x',|s_i|)+1) =
    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
    |s_{i+1}|
  \]

Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game:
  \[
    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
    \leq
    |s_{i+1}| 
  \]
  \[
    <
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
    \leq
    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
  \]
  \[
    <
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
  \]

We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move. Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
  \[
  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
  \]
which we can see here:
  \[
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
    m(x_{i+1},x',|s_{i+1}|) <
    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
  \]

We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids 
  \[
  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
  \]
since
  \[
    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
    |s_{i+1}|
  \]

Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
  \[
    K^*_{S(x_j,x',m(x_j,x',|s_j|)+1)} = 
    K^*_{S(x_j,x',\max(|s_j|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))}
  \]
for $j\leq i$. And when $j<i$,
  \[
    K^*_{S(x_{j+1},x',\max(|s_{j+1}|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))} =
    K^*_{S(x_{j+1},x',|s_{j+1}|)}
  \]
  \[
    \subseteq
    K^*_{S(x_{j+1},x',m(x_{j+1},x',|s_{j+1}|)+1)}
  \]

This concludes the proof.
\end{proof}

\begin{theorem}
$K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
\end{theorem}

\begin{proof}
The proof proceeds similarly to the proof of $K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.

Suppose $\sigma(\<\overline{x},\overline{s}\>,\<y,t\>)$ was a winning $k+1$-tactical strategy, where $\<\overline{x},\overline{s}\>$ represents $\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>$. We may define $S(\overline{x},y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(\overline{x},y,n)<\omega$ such that for each $(\overline{x},y)$,
  \[
    \bigcup_{\overline{s},t \in 2^{\leq n}} \sigma(\<\overline{x},\overline{s}\>,\<y,t\>) \subseteq 
    K^*_{S(\overline{x},y,n)} \cup L_{m(\overline{x},y,n)}
  \]
and so we assume
  \[
    \sigma(\<x,s\>,\<y,t\>) =
    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
  \]

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
\]
is a successful counter to $\sigma$.

We will need the fact that:
  \[
    |s_i| <
    m(x_i,x',|s_i|)+1 =
    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>| 
  \]
  \[
    <
    m(x_i,x',m(x_i,x',|s_i|)+1) =
    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
    |s_{i+1}|
  \]

Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game:
  \[
    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
    \leq
    |s_{i+1}| 
  \]
  \[
    <
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
    \leq
    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
  \]
  \[
    <
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
  \]

We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move. Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
  \[
  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
  \]
which we can see here:
  \[
    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
    m(x_{i+1},x',|s_{i+1}|) <
    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
  \]

We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids 
  \[
  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
  \]
since
  \[
    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
    |s_{i+1}|
  \]

Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
  \[
    K^*_{S(x_j,x',m(x_j,x',|s_j|)+1)} = 
    K^*_{S(x_j,x',\max(|s_j|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))}
  \]
for $j\leq i$. And when $j<i$,
  \[
    K^*_{S(x_{j+1},x',\max(|s_{j+1}|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))} =
    K^*_{S(x_{j+1},x',|s_{j+1}|)}
  \]
  \[
    \subseteq
    K^*_{S(x_{j+1},x',m(x_{j+1},x',|s_{j+1}|)+1)}
  \]

This concludes the proof.
\end{proof}

### 2013-02-04 menger.tex
Finished 2-tactic, started k-tactic on Cantor tree of spaces

  \begin{theorem}
    $X$ is Menger if and only if $S \win \mengame{X}$.
  \end{theorem}

@@

>>>>

  \begin{theorem}
    $X$ is Menger if and only if $C \not\win \mengame{X}$.
  \end{theorem}

@@

  \begin{proposition}
    $X$ is compact if and only if $S \tactwin \mengame{X}$
  \end{proposition}

  \begin{proof}
    Assume $X$ is compact. For each open cover played by $C$, pick the finite subcover.

    Assume $S$ has a winning tactical strategy. For any open cover, have $C$ play only it during the entire game. $S$'s only choice must be a finite subcover.
  \end{proof}

  \begin{proposition}
    If $X$ is $\sigma$-compact then $S \markwin \mengame{X}$
  \end{proposition}

  \begin{proof}
    Let $X=\bigcup_{n<\omega} X_n$ for compact $X_n$. On round $n$, $S$ picks the finite subcover of $C$'s open cover of $X_n$.
  \end{proof}

  \begin{question}
    Does $S \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
  \end{question}

  Let $\sigma(\mathcal{U},n)$ be $S$'s winning Markov strategy.
